\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2019-08-05 popl-2019-journal-v/proving-full-abstraction.tex
[POPLjv] Moderate wording about revoked regions

Kripke future world relations must be defined such that future worlds are extensions of the past world.
In other words, future world relations usually only allow for adding fresh assumptions on fresh memory or protocol steps that the system was designed to support from the start.
However in our setting, we sometimes allow dropping assumptions, namely when linearity tells us that no value in the system depends on assumption anymore.
Specifically, if we have the only linear capability for a piece of memory, then we can be sure that there are no other capabilities for the same memory which makes it safe to repurpose the memory.
In terms of the world, this corresponds to dropping a region and replacing it with a new one.
Due to the fact that future worlds must be an extension of the past world, we cannot drop a region.
Instead, we mark it as revoked which for all intends and purposes corresponds to dropping the region.

>>>>

Kripke future world relations must be defined such that future worlds are extensions of the past world.
In other words, future world relations usually only allow for adding fresh assumptions on fresh memory or protocol steps that the system was designed to support from the start.
However in our setting, we sometimes allow dropping assumptions, namely when linearity tells us that no value in the system depends on assumption anymore.
Specifically, if we have the only linear capability for a piece of memory, then we can be sure that there are no other capabilities for the same memory which makes it safe to repurpose the memory.
We mark dropped regions as revoked in the world following \citet{ahmed_2004} and \citet{thamsborg_2011} which for all intends and purposes corresponds to actually dropping the region.
